
%====================
% EXPERIENCE A
%====================
\subsection{{Web Developer \hfill November 2020 --- Present}}
\subtext{Joules \hfill Market Harborough, Leicestershire / Remote}
\subtext{}
\subtext{}
Currently in my role, my main duties are overseeing junior developers work \& guiding where needed, I also build various new pages and take on new projects, implementing front-end technologies, build and manage the development of python \& impex scripting, optimization and efficiency testing, presenting new and improved workflow processes.
\newline
In this time I have also trained and mentored two junior members of the team, one email developer, the other web developer
\subsection{{Outside day to day}}
\begin{zitemize}
\item Build and configure an image optimization bash script using \href{https://imagemagick.org/index.php}{ImageMagick}.
\item Build and maintain several python automation scripts for our BAU program making build time more efficient.
\item Combine python and impex to create an image block impex for efficiency.
\item Creating a python script for the impexing of images into hybris.
\item Switching from image to picture tags in all BAU for optimization.
\item Addition of webp to the bash image script for optimization using HTML picture tags
\item Improving grunt workflow, saving time where i can on load time.



\end{zitemize}
%====================
% EXPERIENCE A
%====================
\subsection{{Junior Web Developer \hfill May 2018 --- November 2020}}
\subtext{Joules \hfill Market Harborough, Leicestershire}
\subtext{}
\subtext{}
In my first two years at Joules, my main focus was working on the e-commerce sites \& email development, working closely with in-house design team to make sure work was completed to an accurate level, optimization is also a big passion of mine, so built a script using python for automation for efficiency on build time for our BAU projects. 
\newline
After my manager left I was then head of the email program, which was also automated in python, we had a set modular library, which allowed us to build all emails efficiently, with strict brand guide lines.

%====================
% EXPERIENCE B
%====================
\subsection{{Junior Front-End Web developer \hfill June 2017 --- May 2018}}
\subtext{Wholesale LED lights \hfill Leicester}
\begin{zitemize}
\item Lead Front-End in house developer, building and maintaining Magento E-commerce websites.
\item Creating responsive websites from scratch to drive traffic towards the company new business ideas.
\item Adhering to best practice working standards for version control via Github. Following the current rule sets and ensuring that the staging and production environments are respected.
\item Following strict coding standards, this includes commenting, indentation and logic.
\item Improving the design of the website and improve usability.
\item Optimization of legacy code.
\end{zitemize}

%====================
% EXPERIENCE C
%====================
\subsection{{Junior Front-End Web Developer \hfill June 2016 --- June 2017}}
\subtext{Auction Marketer \hfill Sywell, Northamptonshire}
\begin{zitemize}
\item Building and maintaining the Auction Marketer online bidding software for a vast client base.
\item To adhere to best practice working standards for version control via Github whilst following set rules and ensuring that the development, staging and live environments are respected.
\item To ensure the organization and management of workload is in line with the current project/production scheduling using the supplied set of tools, Asana and Harvest ad to be aware of current agile processes and workflow for web based software development.
\item To ensure that any work that needs to be performed in any of the base product builds is properly rolled into existing or in development client builds, and that version control notes are properly written up.
\item Following a rigorous testing regime including cross platform, cross browser and responsive testing.
\item To continually develop a reduced friction model for the rollout of the base products, lite, classic and enterprise with a view to maximize profitability of the business unit and reduce reworking and launch bug fixes.
\item To accept ownership of workload from start to finish and be accountable for delivery to best quality standards making sure the client is never exposed to poor quality or poorly tested work. And documenting that work has been tested before passing for client approval.
\item Regular team meetings to discuss development, strategy and the best course of action to tackles new projects
\item Accepting ownership of workload from start to finish and be accountable for delivery to best quality standards where the customer must never be exposed to poor quality or poorly tested work and documenting that work has been tested before passing for client approval.
\item Working with the team to develop continuous product excellence through knowledge sharing and product documentation and reducing friction points in the roll out of product/features/upgrades to make processes as simple and reliable as possible.
\item Maintaining consistent communication with other team members to ensure that customer requirements are met, delivered on time and that any delays, problems or issues are clearly communicated to management.
\item Thoroughly test all work to ensure that design is matched and works across all browsers and devices. To test work for functional correctness and to consider key customer journeys and usability and develop and improve product testing plans and auto testing to deliver continual product improvement.
\end{zitemize}
 